### 2018-09-17 Chapters/Chapter3.tex
add apendix 3a\
commit

Which is the Hamiltonian \ref{Hubbard} without DMI interaction. We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)}$, where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$. The electric field has the form $\bs{E}(t) = E_0 \sin (\omega t)\bs{\hat{x}}$ (one-dimensional lattice). We can therefore take $\bs{A}(t) = -\frac{E_0}{\omega}\cos(\omega t)\bs{\hat{x}} = -\bs{A}\cos(\omega t)$. Therefore the time dependent Hamiltonian is:

@@

>>>>

Which is the Hamiltonian \ref{Hubbard} without DMI interaction. We can introduce a time dependent electric field in this Hamiltonian by adding a phase to the hopping term $t_{ij}(t) = t_0e^{ie\bs{R}_{ij}\bs{A}(t)}$, where $\bs{A}$ is the vector potential and $\bs{R}_{ij} = \bs{R}_i-\bs{R}_j$. This is known as Peierls substitution and it is derived in \ref{AP3A}. The electric field has the form $\bs{E}(t) = E_0 \sin (\omega t)\bs{\hat{x}}$ (one-dimensional lattice). We can therefore take $\bs{A}(t) = -\frac{E_0}{\omega}\cos(\omega t)\bs{\hat{x}} = -\bs{A}\cos(\omega t)$. Therefore the time dependent Hamiltonian is:

@@

\end{section}

\begin{subappendices}
\begin{section}{Peierls Substitution}
\label{AP3A}

In first quantization we can introduce a vector potential $\bs{A}(\bs{r},t)$ by changing the Hamiltonian of the latice \ref{LaticeHam} to:

\begin{equation}
  \hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r})
\end{equation}

Now the Bloch functions defined for \ref{LaticeHam} will not be eigenfunctions of this Hamiltonian. We will show that the functions:

\begin{equation}

\end{equation}

\end{section}
\end{subappendices}
